%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{profile}
\name{Alejandro}{Mantilla}
\position{DATA SCIENCE{\enskip\cdotp\enskip}DATA ENGINEERING{\enskip\cdotp\enskip}BUSINESS INTELLIGENCE{\enskip\cdotp\enskip}SOFTWARE DEVELOPMENT}
%\address{Bogotá, Colombia}

\chesscom{AlejoMantilla}{1088}
\email{alejomantilla@protonmail.com}
\homepage{mantimantilla.github.io}
\github{MantiMantilla}
\linkedin{Alejandro Mantilla}{alejandro-mantilla-redondo}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}

%\quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient{Chess.com {-} Data Engineer}{Chess.com}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Cover Letter {-} Data Engineer}
% How the letter is opened
\letteropening{Dear Chess.com recruiting team, I am writing to express my strong interest for the position of Data Engineer.}
% How the letter is closed
\letterclosing{Thank you for considering my application! I hope we find the opportunity to discuss in greater detail how my profile aligns with Chess.com's requirements and in which ways I may be able to contribute to foster a data-centric and collaborative culture.\\Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter{\today}{ALEJANDRO MANTILLA\quad·\quad COVER LETTER}{}

% Print the title with above letter information
\makelettertitle{}

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

	\lettersection{About me}

  My name is Alejandro Mantilla and I am a Data Enginner with 7 years of experience, 2 of which are in the gaming industry (BetOnline), where I developed and maintained data solutions for the BI and fraud teams. I have Bachelor and Master of Science degrees in industrial engineering (with a focus on data science), as well as a minor in mathematics. It is my passion for creating an impact through engineering and mathematics that drove me to become a teacher at my university, where for three years I taught at a postgraduate level and researched topics in data engineering, machine learning, and software development. Particularly, my research at the university was made with the objective of enabling researchers to develop and deploy data-driven tools to the cloud. Academic interests aside, I have practical experience in data engineering and business intelligence from the time I spent working at Intel Corporation. There, I was able to thoroughly influence our sales and marketing strategies, not only through deep insights into our data, but also by building and managing data technologies such as databases, data pipelines, dashboards, and web applications.

	Regarding my professional path, I spend a significant amount of time learning and sharpening my technical and analytical skills, to the point that I take pride in my problem-solving, be it strategic or technical. Several of the projects initiated by me have seen great success despite the difficulty to integrate them into settled organizations such as my university, Intel, or BetOnline. For example, I have taken advantage of my knowledge of cloud computing, web development, and data science to create interactive tools that allow the fraud team to efficiently act on fraud alerts, keep track of relevant metrics, forecast income and expenses, and experiment with fraud prevention strategies. It is my commitement to myself to consistently improve as an engineer and to always bring something new and of impact to my peers.

  I am always looking to learn and exercise my mind: I enjoy learning new languages which is why I speak Spanish, English, and German fluently (currently learning Chinese); I enjoy practicing sports, of which I enjoy kitesurfing the most. I have yet to become a great chess player, but since learning to play about a year and a half ago, I've been consistently playing, alway looking to improve, it might not be much, but that 1000 rapid ELO means a lot to me! I don't want to spend too much time learning openings, and would rather study my middle game, though I do play into the Vienna Gambit when I get the chance. I frequently visit my local chess club, and can't get enough of meeting people passionate about their hobbies (chess or otherwise)!.


	\lettersection{Why Chess.com?}

	I am drawn to Chess.com due to its admirable commitment to develop a welcoming chess community, through services that would be fascinating to make work at scale. I strongly believe that Chess.com's requirements to strengthen its data infrastructure and strategy are a good fit for my skills, experience, and passion for sustainable information practices, be it to orchestrate data pipelines with Airflow or to build data services with dbt.

	Throughout the years I've faced several engineering challenges which soon taught me that what I enjoy the most is to learn learn from the creation process. Be it developing software, building mechanical contraptions or clumsily improvising on my guitar, I will always aim to create something new. I believe that Chess.com can provide an environment that could nourish this commitment to innovate, as well as grant me access to new knowledge in the topics of Big-Data, enterprise data practices, and data compliance and governance, which I find intriguing.


	\lettersection{Why me?}

	Throughout my academic and professional journey, I have developed a robust skillset that aligns well with the requirements of the data engineer role. My proficiency in, Python, Spark, dbt, SQL, Airflow, and several dashboarding tools has allowed me to effectively design, deploy, and manage essential tools to the operation of organizations I've been part of. I have leveraged these skills in my previous roles to streamline processes, improve operational efficiency, and enable informed decision-making.

	What sets me apart is my genuine passion for data quality, machine learning, big-data, and providing business insights. This commitment is evident in my academic pursuits, personal lifestyle, and practical experience. I have delved deeply into the industry practices to exploit internal and external data sources, and identified that which I agree with the most, often advocating for the technologies that enable a true commitment to long-term impact. By approaching problems from a data-driven perspective, I have successfully identified opportunities for organizations to adopt practices that allow them to keep track of and directly influence their performance metrics and KPIs.

	Furthermore, my experience as a teacher has helped my hone my ability to effectively communicate complex ideas and concepts to diverse audiences. I have had the privilege of sharing my knowledge and fostering a learning environment that promotes critical thinking and the development of problem-solving skills. These teaching experiences have strengthened my ability to collaborate with cross-functional teams, adapt to different work styles, and drive consensus among stakeholders.
\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing{}

\end{document}
